\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}

### 2023-08-18 doc/paper/supplements.tex
Updates from Overleaf

\title{\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip
Transmission of airborne respiratory infections with and without air cleaners in a Swiss school during non-pandemic conditions: A modeling study of epidemiological, environmental, and molecular data}}

% author list
\author[1$\ddag$]{Nicolas Banholzer}
\author[2]{Philipp Jent}
\author[3]{Pascal Bittel}
\author[3]{Lavinia Furrer}
\author[1]{Matthias Egger}
\author[4]{Tina Hascher}
\author[1*]{Lukas Fenner}

\affil[1]{Institute of Social and Preventive Medicine, University of Bern, Bern, Switzerland}
\affil[2]{Department of Infectious Diseases, Inselspital, Bern University Hospital, University of Bern, Bern, Switzerland}
\affil[3]{Institute of Infectious Diseases, University of Bern, Bern, Switzerland}
\affil[4]{Institute of Educational Science, University of Bern, Bern, Switzerland}

@@

>>>>

\title{\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip
Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}}

% author list
\author[1$\ddag$,2]{Nicolas Banholzer}
\author[2,3]{Philipp Jent}
\author[2,4]{Pascal Bittel}
\author[4]{Lavinia Furrer}
\author[4]{Alban Ramette}
\author[4]{Ronald Dijkman}
\author[5]{Jenna Kelly}
\author[1]{Kathrin Zürcher}
\author[1]{Matthias Egger}
\author[2,6]{Tina Hascher}
\author[1*,2]{Lukas Fenner}

\affil[1]{Institute of Social and Preventive Medicine, University of Bern, Bern, Switzerland}
\affil[2]{Multidisciplinary Center for Infectious Diseases, University of Bern, Bern, Switzerland}
\affil[3]{Department of Infectious Diseases, Inselspital, Bern University Hospital, University of Bern, Bern, Switzerland}
\affil[4]{Institute of Infectious Diseases, University of Bern, Bern, Switzerland}
\affil[5]{Interfaculty Bioinformatics Unit, University of Bern, Bern, Switzerland}
\affil[6]{Institute of Educational Science, University of Bern, Bern, Switzerland}

@@

\section{Modeling changes in cough frequency}\label{sec:aud-regression-model}

We analyze the daily number of coughs $Y$ with a Negative Binomial regression model
\begin{align*}
    Y | \beta_0, \beta_1, \dots, \beta_6 &\sim \text{Negative-Binomial}(\mu,\phi) \\
    \log \mu &= \log T + \beta_0 + \beta_1 \cdot \text{AirCleaner} + \beta_2 \cdot \text{Class} + \beta_3 \cdot \text{Weekday} + \beta_4 \cdot \text{Students} + \beta_5 \cdot \text{Ventilation} + \beta_6 \cdot \text{Cases} \\
    \beta_0 &\sim \text{Student-t}_5(0, 2.5) \\
    \beta_1, \dots, \beta_6 &\sim \text{Student-t}_5\left(0, \frac{2.5}{s_{x}}\right) \\
    \frac{1}{\sqrt{\phi}} &\sim \text{Half-Normal}(0,1),
\end{align*}
where $T$ is the daily duration that students were in the classroom and $\phi$ is the parameter modeling over-dispersion in count data.
